Robotic Grasping in Clutter Using a Hierarchy of Supervisors for Deep Learning from Demonstrations

### 2016-03-16 paper.tex
.
Edit pass.

\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$,Wesley Hseih$^1$,Florian T. Pokorny,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\begin{abstract}
Online learning from demonstration algorithms such as
DAgger can learn policies for problems where the system dynamics and
the cost function are unknown. However they impose a
burden on supervisors to respond to queries each time the robot
encounters new states while executing its current best policy.  Traditionally there has only been one supervisor and it is an expert. However, an expert supervisor is a costly resource that could be impractical for large scale learning tasks. However, there an expert supervisor might not be needed for a large portion of the state space , which could be handled by less-skilled supervisors. We present the Gambler's DAgger, which instead of only using an expert supervisors presents a hierarchical supervisor model, that first leverages cheaper supervisors, such as analytical methods on approximate dynamics or crowdsourced Amazon Mechanical Turk workers to train the policy. Then only consults an expert supervisor for harder to learn states. We demonstrate this approach in training a visuomotor deep network policy in TensorFlow for grasping in clutter on a 4-DOF Zymark Robot. We were able to reduce the number of queries to the final expert supervisor by $X$ and manage to collect $X$K examples by leveraging the hierarchical supervisor model. 
 \end{abstract}

@@

\section{Introduction} 
Consider a robot trying to reach an object on a cluttered shelf in a shipping warehouse, as illustrated by the Amazon Picking Challenge at ICRA 2015 \cite{mahler2016dexnet}, this is an important task for being able to efficiently ship and process orders.   The robot is presented with a visual feed of the environment and must plan a series of motions to push the cluttered obstacles and grasp a goal object. A challenge could arise  when the robot encounters an unknown obstacle object that it does not have a known dynamics  for and must manipulate the environment to reach goal.

One solution is to learn a manipulation policy across a variety of obstacle objects and try to generalize this approach to unknown obstacle in the environment. Reinforcement learning techniques are capable of being applied to this problem, however they could require a large amount of trials on the robot to accomplish the task when the dynamics are unknown and the state space is high dimensional image data~\cite{pinto2015supersizing}.

Rather than using an unsupervised learning approach, we propose guiding the robot how on to interact with the environment via a supervisor, who knows how to accomplish the task~\cite{argall2009survey}. Learning from demonstration (LfD) algorithms, which have been used successfully in recent year for a large number of robotic tasks, including helicopter maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot surgery~\cite{van2010superhuman}, is a form of how to provide this guidance.

 \begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{Typical Initial States for our grasping in clutter task with a Zymark Robot. Red shapes indicate the clutter objects and the yellow circle indicates the goal object. The robot learns from 250x250 RGB image data to push the shapes and reach the yellow circle through our algorithm A Gambler's DAgger.}
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

LfD algorithms can be categorized as offline, where the robot only observes demonstrations, or online, where the robot interacts with the world and receives feedback from the supervisor.
In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.  During execution, a small control error can accumulate, leading the robot away from the region of the state space where it was given examples, leading to unrecoverable failures.  For example, a robot  trained on examples driving safely down the center of a lane, but even slight deviations will eventually put the robot into states near the side of the road where its policy could  fail~\cite{pomerleau1989alvinn}. Ross and Bagnell showed the number of errors made by the robot, in the worst case,  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.

Online LfD addresses this issue by iteratively requesting more examples from the supervisor in states the robot encounters~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. One such algorithm, DAgger, learns a series of policies. At each iteration, the robot computes a policy based on the existing examples, then rolls out (executes) that policy, and the supervisor provides demonstrations for all states the robot visits. The new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. In DAgger, under certain conditions, the number of errors scales only linearly with the time horizon of the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot visits during training.  Traditionally there has only been one supervisor and it is deemed an expert ~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. However, when learning complicated tasks with high stochasticity in the environment this could require a large amount of the expert's time, which is a costly resource.

Learning can be bootstrapped with a sequence of increasingly skilled supervisors. In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object. Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.

We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost: analytical models, crowd-sourced workers and an expert supervisor to learn the robot grasping in clutter task. We demonstrate this approach by training a deep neural network for the visuo-motor based task of  grasping in clutter on a Zymark Robot. Our robot consists of an 2DOF arm and a gripper that lie in a planar workspace. The objects dataset consists of 20  extruded polygons taken from 2D projections of objects in the Dex-Net \cite{mahler2016dexnet} database.  Results show that by leveraging a hierarchy of less skilled experts, the total amount of cost incurred is reduced by X$\%$ and the task is $61\%$ successful on our test set of 20 object configurations of shapes not trained on \mlnote{need to think of a better teaser statement}

\section{Related Work}
Below we summarize related work in Robotic Grasiping in Clutter,  Online LfD setting and then the field of Curriculum learning, which is similar to the concept of hierarchical supervisors.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping has been extensively studied over the
past four decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.  However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp ~\cite{katz2008can}.
Prior work has addressed integrated perception and grasping
in clutter where the objective is to grasp objects in an
unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these
methods do not specifically aim to grasp a single target object
in clutter. 
Leeper et al. ~\cite{} use a human operator for assistance to guide the
robot through clutter with the objective of grasping a target
object. However, the robot required the human to be present at all times and did not attempt to learn to operate autonomously.We are interested in only querying the supervisor for examples until the robot is successful at the task.

Prior work has studied the issue of manipulating objects
by performing pushing operations~\cite{}. Berenson et
al. ~\cite{} use a sampling-based planner that considers clearance
from obstacles in the environment to plan a grasp
approach trajectory in cluttered environments. Cosgun et al.
[3] and King et al. \cite{kingnonprehensile} consider the problem of planning
a series of push operations that would place an object at a
desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers \cite{kitaevphysics}. However, all of these works assume a known model of the world is given to them, we are interested in learning manipulation polices via leveraging an supervisors intuition for the the task.  \mlnote{We should discuss how to distinguish our work (Properties of our approach are we assume raw image data, real time and unknown dynamics)}.

\noindent \textbf{Online Lfd with an Expert Supervisor}
Successful robotic examples of Online Learning From Demonstration where an expert has been employed in flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.

However, to date these approaches have all used only one expert supervisor to provide examples for all parts of the state space. Our contribution consists of the use of a hierarchical structure of different skill level supervisors to reduce learning cost.

\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reducing queries to the supervisor is applying active learning to only ask for queries one the robot is uncertain about the correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have been applied by \cite{chernova2009interactive,judah2011active,grollman2007dogged}

However, Kim et al. demonstrated that due to the non-stationarity of the problem traditional active learning techniques may not work because the underlying state distribution changes and thus the use of novelty detection is needed to be more conservative in determining uncertainty~\cite{kim2013maximum}. Laskey et al. introduced SHIV, for using active learning tailored to high dimensional and non-stationarity state distributions and  provided a modified version One Class SVM to reduce the from density estimation, which requires regression, to the simpler regularized binary classification ~\cite{laskey}.

Novelty detection being needed to reduce supervisor burden via active learning implies that for problems with high stochasticity, such as grasping in clutter, the expert would be queried a significant number. Furthermore, we are interested in using deep neural architectures to learn task specific features for the task. SHIV applies novelty detection in a known feature space, however the feature space now changes each iteration. Thus, it is not straightforward to apply existing techniques.

\noindent\textbf{Curriculum Learning}
\mlnote{TODO: add more curriculum}
Our approach is similar to the area known as curriculum learning, where a neural network is trained via first  easier to learn examples and then gradually increasing the difficulty of the examples to learn ~\cite{bengio2009curriculum}.

Sanger et al. used curriculum learning in robotics to gradually train a neural network policy to learn the inverse dynamics of a robot manipulator. They then varied then data collection scheme such that easily learned trajectories where shown first and then gradually increased the difficulty~\cite{sanger1994neural}.

Our approach is different than curriculum learning in that a supervisor can be provide low quality examples in parts of the state space visited by the robot, which means it isn't neccesarily easier for the robot to learn one supervisor's policy versus another in the hierarchy. Combining hierarchical supervisors and curriculum learning could be a promising avenue for future work though.

\section{Problem Statement}
The goal of this work is to learn a policy that matches that of an expert supervisor's while asking expert supervisor with fewer queries than DAgger.

@@

\noindent\textbf{Policies and State Densities.}
Following conventions from control theory, we denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of 
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We denote by $\mathcal{U}$ a set of allowable control inputs for the robot, which can be discrete or
continuous. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume an unknown probability density over initial states $p(\bx_0)$.
%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.

A demonstration (or trajectory )$\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
${\tau} = (\bx_0,....,\bx_T)$.

@@

While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, when 'rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

\noindent\textbf{Objective.} The objective of  policy learning is to find a policy that maximizes some known cumulative reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The reward $r:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in the task of inserting a peg into a hole, a function on distance between the peg's current and desired final state is used~\cite{levine2015end}.

The reward function  for a task like grasping in clutter, (i.e.  successfully grasping the goal object) is delayed \cite{kitaevphysics}. The idea behind DAgger and SHIV is to query a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$. This induces a training data set $\mathcal{D}$ of state-control input pairs.

We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
measure between any pair of control values. In the continuous case, we consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$,
while in the discrete case $l(\bu_0,\bu_1) = 1$ if $\bu_0 \neq \bu_1$ and $l(\bu_0, \bu_1)=0$ otherwise.

Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how `close' the robot's policy's
returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is to produce a policy that minimizes the surrogate loss.

Following~\cite{ross2010reduction}, our objective is to find a policy $\pi_{\theta}$ minimizing the expected surrogate loss with respect to the most skilled supervisor, where the expectation is taken over the distribution of states induced by the policy across any time point in the horizon:

@@

 If the robot could learn the policy  perfectly, this state density would match the one encountered in user examples. But if the robot makes an error, that error changes the distribution of states that the robot will visit, which can lead to states that are far away from any examples and difficult to generalize to~\cite{pomerleau1989alvinn}. This motivates iterative algorithms like DAgger, which iterate between learning a policy and the supervisor providing examples.

We  introduce the concept of their being a set of supervisors each with an associated cost and skill level. Denote $\tilde{\pi}_M$ the most skilled and costly supervisor in this set. This supervisor could for example be a person with a Phd in machine learning and robotics. We formally define how each supervisor in the set is related to each other in Sec. \ref{sec:hS}.  Every time a supervisor is queried a cost, $C_m$, is incurred this could be an hourly pay rate or computational time.

While Eq. \ref{eq:LFD_obj} is the primary objective of our algorithm a secondary objective is to reduce the cumulative cost associated with training the robot. Thus, we are interested in solving the following objective

 \vspace{-2ex}
\begin{align}\label{eq:bugjet_LFD_obj}
\underset{\theta,C_{m,j}}{\min} \: & \sum^J_{j=1} C_{m,j}\\
 \mbox{s.t.} \: &E_{p(\bx|\theta)} [l(\pi_\theta(\bx),\tilde{\pi}_M(\bx))] \leq \epsilon
\end{align}

where $J$ is the number of queries need to satisfy the constraint on expected surrogate loss, $C_{m,j}$ denotes the cost incurred by querying the supervisor at that iteration and $\epsilon$ is a user-defined threshold on how close robot policy is to match the highest quality supervisor. We present our algorithm, LEATHERMAN, which aims to solve Eq. \ref{eq:bugjet_LFD_obj}.

 \section{Algorithm}
 In this section, we first recall the original DAgger algorithm. Then introduce the notion and formal definition of a hierarchical supervisor and finally describe how to combine DAgger with a hierarchical supervisor to create a Gambler's DAgger.

 \subsection{DAgger: Dataset Aggregation}
 DAgger~\cite{ross2010reduction} solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.

@@

 \subsubsection{Step 2}
The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}

>>>>

\title{Robotic Grasping in Clutter Using a Hierarchy of Supervisors for Deep Learning from Demonstrations}

\author{Michael Laskey$^1$, Jonathan Lee$^1$, Caleb Chuck$^1$, David Gealy$^1$, Wesley Hseih$^1$, Florian T. Pokorny,\\
 Anca D. Dragan$^1$, and Ken Goldberg$^{1,2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh,ftpokorny,anca\}@berkeley.edu, \small staszass@rose-hulman.edu} }%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\begin{abstract}
Recent progress in learning from demonstrations increasingly indicates that robots can acquire manipulation skills from
large collections of training data. Online learning from demonstration algorithms such as DAgger can in particular learn
policies for problems where the system dynamics and the cost function are unknown. Traditionally, these systems have
been trained by skilled human supervisors providing feedback on the current learned policy. As the number of
demonstrations increases, this approach can however incur a substantial time and labor cost. We study the grasping in
clutter problem and propose a hierarchical approach to learning from demonstrations based on DAgger which also
incorporates a deep learning architecture to learn policies directly from video sequences. In experiments with a 4-DOF
Zymark Robot, we consider a hierarchy of three increasingly competent and costly supervisor types: an analytical grasp
planner, a crowd-sourced human workers and a human expert supervisor. Our results indicate that training a policy
hierarchically by bootstrapping with the analytical method, followed by crowd sourced and expert supervision improves
test-time performance compared to training only with an expert supervisor by XX while reducing training cost by XX. We
furthermore find that the addition of crowd-sourced supervisors compared to analytic pre-training followed by
supervision by an expert improves performance significantly. [FP: Fine tune how we report main results here]
 \end{abstract}

@@

\section{Introduction} 
As illustrated by the recent Amazon Picking Challenge at ICRA 2015, the grasping in clutter problem, where a robot needs
to grasp an object that might be occluded by other objects in the environment poses an interesting challenge to robotic
systems. Two fundamental approaches to grasping in clutter include the analytic model driven approach \cite{1,2,3},
where the interaction dynamics between the robot and obstacles are formulated analytically. However, modeling all the 
physical properties of interaction poses a highly challenging problem due to uncertainty in modeling parameters such as
inertial properties and friction.

An alternative approach, which we propose here, is to approach the grasping in
clutter problem in a model-free manner, where the interaction behavior is learned directly from data within the learning
from demonstrations framework \cite{argall2009survey}. Learning from demonstration (LfD) algorithms have been used
successfully in recent years for a large number of robotic tasks, including helicopter
maneuvering~\cite{abbeel2007application}, car parking~\cite{abbeel2008apprenticeship},  and robot
surgery~\cite{van2010superhuman}. Furthermore, deep learning, which we use to learn policies directly from raw video
data, has emerged as a highly versatile technique used for this purpose ~\cite{pinto2015supersizing}.

\begin{figure}
\includegraphics[width=0.5\textwidth]{f_figs/teaser.eps}
\caption{
Three roll-outs of a fully trained grasping in clutter policy (one per column, bottom to top) which was trained using a
hierarchy of three supervisors consisting of analytical motion planning, crowd-sourcing and human expert. 
Red shapes indicate clutter objects and the robot is trained to reach the yellow circle. {\color{blue}FP: how about we
display the policy after each of the three training steps? One per column}}
\vspace*{-20pt}
\label{fig:teaser}
\end{figure}

%LfD algorithms can be categorized as either \emph{offline}, where the robot only observes a set of finalized
%demonstrations, or \emph{online}, where the robot rolls out a current policy and then receives feedback from the supervisor.
%In offline LfD, the robot learns the policy based on a batch of examples, and then executes it to achieve the task.  During execution, 
%control error can accumulate, leading the robot away from the region of the state space where it was provided with
%training data, leading to unpredictable behavior. For example, an autonomous car trained on examples of a cars driving
%near the center of a lane might, due to deviations encounter new states far away from previously trained examples that
%can result in failures~\cite{pomerleau1989alvinn}. For a class of supervised learning methods, Ross and Bagnell showed
%that the number of errors made by the robot, can scale quadratically with the time horizon of the task, in particular~\cite{ross2010efficient}.

Our approach is based on online Learning from Demonstrations (LfD) where a robot iteratively learns a policy and is
provided by feedback on the current policy roll out by a supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. 
We build on, DAgger, an online LfD algorithm which at each iteration, computes a policy based on prior demonstrations,
and then rolls out that policy. A supervisor then provides control signals as feedback on the current policy
and new state/control examples are aggregated with the prior examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. 
Ross et al. showed that DAgger, under a no-regret assumption, can be guaranteed to deviate from the supervisor's policy with an error
at most linear in the time horizon for the task~\cite{ross2010reduction}.

One drawback is that DAgger imposes a substantial burden on the supervisor, who must label all states that the robot
visits during training.  Traditionally there has only been one supervisor and it is deemed an expert
~\cite{ross2010efficient,ross2010reduction,ross2013learning,duvallet2013imitation}. In this work, we propose to instead
utilize a hierarchy of supervisors that exhibit increasing cost and competence at a given task to incrementally
bootstrap the learning process. At the lowest level of the hierarchy, we in particular consider an analytic motion
planner which acts as an affordable supervisor.

%Learning can be bootstrapped with a sequence of increasingly skilled supervisors. In our grasping in clutter example, the robot spends a large portion of the time learning how to go towards the goal object. Analytical techniques such as forward kinematics, template matching and motion planning are readily available to provide examples in these parts of the state space.

%We propose bootstrapping a policy from a hierarchy of supervisors ranked by cost: analytical models, crowd-sourced workers and an expert supervisor to learn the robot grasping in clutter task. We demonstrate this approach by training a deep neural network for the visuo-motor based task of  grasping in clutter on a Zymark Robot. Our robot consists of an 2DOF arm and a gripper that lie in a planar workspace. The objects dataset consists of 20  extruded polygons taken from 2D projections of objects in the Dex-Net \cite{mahler2016dexnet} database.  Results show that by leveraging a hierarchy of less skilled experts, the total amount of cost incurred is reduced by X$\%$ and the task is $61\%$ successful on our test set of 20 object configurations of shapes not trained on \mlnote{need to think of a better teaser statement}

\section{Related Work}
Below, we summarize related work in Robotic Grasiping in Clutter, the Online LfD setting and then the field of
Curriculum learning, which is related to the concept of hierarchical supervisors.

\noindent \textbf{Robotic Grasping in Clutter}
Robotic grasping is a well-established research topic in robotics that has been studied for several
decades~\cite{bicchi2000robotic}. A significant amount of prior work focuses on planning grasps given a known object.
However, in unstructured environments clutter poses a significant challenge for reaching the planned grasp
~\cite{katz2008can}. Prior work has addressed integrated perception and grasping in clutter where the objective is to
grasp objects in an unorganized pile ~\cite{pinto2015supersizing,nieuwenhuisen2013mobile}, but these methods do not
specifically aim to grasp a single target object in clutter. Leeper et al. ~\cite{} use a human operator for assistance
to guide the robot through clutter with the objective of grasping a target object. However, the robot required the human
to be present at all times and did not attempt to learn to operate autonomously. We are interested in a data-driven
approach that only queries a supervisor at training time and which can operate autonomously thereafter.

Prior work has studied the problem of manipulating objects
by performing pushing operations~\cite{}. Berenson et
al. ~\cite{} in particular use a sampling-based planner that considers clearance
from obstacles in the environment to plan a grasp
approach trajectory in cluttered environments. Cosgun et al.
[3] and King et al. \cite{kingnonprehensile} consider the problem of planning
a series of push operations that move an object to a
desired target location. Kiteav et al. planned a trajectory in a physics simulator using LQG based controllers
\cite{kitaevphysics}. However, all of these works assume a known model of of the object behavior is provided. We are
interested in learning manipulation polices in a data-driven manner instead, leveraging a hierarchy of supervisors for
training.  
\mlnote{We should discuss how to distinguish our work (Properties of our approach are we assume raw image data, real time and unknown dynamics)}.

\noindent \textbf{Online Lfd with an Expert Supervisor}
Successful robotic examples of Online Learning From Demonstration with an expert supervisor include applications to flying a quad-copter through a forest, navigating a wheel chair across a room and teaching a robot to follow verbal instructions and surgical needle insertion \cite{ross2013learning, kim2013maximum, duvallet2013imitation, laskey}.

However, to date, these approaches have used only one expert supervisor to provide training data for all parts of the
state space. We propose to instead utilize hierarchy of supervisor of different skill level and cost to reduce the
overall learning cost.

\noindent\textbf{Reducing Supervisor Burden in Online LfD} One approach that has been studied to reduce the number of
supervisor supervision is to apply active learning to only ask for supervision when the robot is uncertain about the
correct control to apply. Traditional active learning techniques like query-by-committee and uncertainty sampling have
in particular be utilized for this purpose \cite{chernova2009interactive,judah2011active,grollman2007dogged}

However, Kim et al. demonstrated that due to the non-stationarity of the distribution of states encountered during
learning, the traditional active learning techniques may be suitable since the underlying state distribution changes.
Thus the use of novelty detection was proposed~\cite{kim2013maximum}. Laskey et al. introduced SHIV, using an active
learning approach tailored to high dimensional and non-stationarity state distributions and a modified version of the
One Class SVM classifier. This enabled the authors to reduce the density estimation problem to a 
simpler regularized binary classification~\cite{laskey}. However the grasping in clutter problem exhibits a high amount
of stochasticity requiring a large training data set which poses a significant computational challenge to these methods.
In the present paper, we hence consider using Deep Learning, as an underlying scalable learning algorithm in combination
with DAgger.

\noindent\textbf{Curriculum Learning}
Our approach is closely related to ideas from \emph{curriculum learning}, where a neural network is trained via 
incrementally, first on easier examples and then gradually on data of increasing difficulty~\cite{bengio2009curriculum}.

Sanger et al. used curriculum learning in robotics to gradually train a neural network policy to learn the inverse
dynamics of a robot manipulator. They then considered a collection scheme where easily learned trajectories where shown
to the robot first and then gradually increased the difficulty~\cite{sanger1994neural}.

Our approach is different from curriculum learning in that a supervisor may occasionally provide low quality examples in
parts of the state space visited by the robot, which implies that it is now necessarily easier for the robot to learn
one supervisor's policy versus another in the hierarchy. In future work, we intend to study potential combinations of
hierarchical supervisors and curriculum learning which we believe could provide a promising avenue for research.

\section{Problem Statement}
Given a collection of increasingly able and costly supervisors $S_1, \ldots, S_M$, the goal of this work is to learn a
policy that closely matches that of the most able supervisor $S_M$ while minimizing the overall cost of training a
policy. We formalize this approach as follows.

@@

\noindent\textbf{Policies and State Densities.}
Following conventions from control theory, we denote by $\mathcal{X}$ the set of observable states for a robot task, consisting, for example, of 
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We denote by $\mathcal{U}$ the set of allowable control inputs for the robot. $\mathcal{U}$ may be discrete or
continuous in nature. We model dynamics as Markovian: the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ depends only oni the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume an unknown probability density over initial states $p(\bx_0)$.

A demonstration (or trajectory) $\hat{\tau}$ is a series of $T+1$ pairs of states visited and corresponding
control inputs at these states, $\hat{\tau} = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_t\in \mathcal{X}$
and $\bu_t\in \mathcal{U}$ for $t\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
For a given trajectory $\hat{\tau}$ as above, we denote by ${\tau}$ the corresponding trajectory in state space,
${\tau} = (\bx_0,....,\bx_T)$.

@@

While we do not assume knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, 'rolling out' trajectories under a policy
$\pi_{\theta}$ in our experiments, we utilize the robot to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

{\color{blue} FP: might make this and the above specific to grasping in clutter?}
\noindent\textbf{Objective.} The objective of policy learning is to find a policy that maximizes some known cumulative
reward function $\sum^T_{t=1} r(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The reward $r:\mathcal{X}\times
\mathcal{U}\to \mathbb{R}$ is typically user defined and task specific \cite{1,2,3}. 
For example, in the task of inserting a peg into a hole, a function quantifying a notion of distance between the peg's
current and desired final state can be used~\cite{levine2015end}.

Since grasp success is typically considered as a binary reward which is observed only at a delayed final state \cite{kitaevphysics}, 
grasping in clutter poses a challenging problem for traditional reinforcement learning methods. We hence instead build
upon DAgger which queries a supervisor for appropiate actions, to provide the robot a set of N stochastic demonstrations trajectories $\lbrace \hat{\tau}^1,...\hat{\tau}^N \rbrace$. This induces a training data set $\mathcal{D}$ of state-control input pairs. 
We define a `surrogate' loss function as in~\cite{ross2010reduction}, $l:\mathcal{U}\times \mathcal{U}\to \mathbb{R}$, which provides a distance
measure between any pair of control values. We consider $l(\bu_0,\bu_1) = ||\bu_0-\bu_1||^2_2$.

Given a candidate policy $\pi_{\theta}$, we DAgger uses the surrogate loss function to approximately measure how `close' the robot's policy's
returned control input $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. The goal is of DAgger is to produce a policy that minimizes the expected surrogate loss:

@@

Instead of a single supervisor $S$, which classically is considered to be a skilled human teacher, we instead consider a
hierarchy $S_1, \ldots, S_M$ of supervisors which we may be algorithms or humans and which follow policies $\pi_1, \ldots, \pi_M$ with
associated expected cumulative rewards $R_i$ satisfying $R_1\le R_2 \le \ldots \le
R_M$. Furthermore, we assume that the cost associated to providing a state
label for supervisor $S_i$ is $C_i$ with $C_1\le C_2 \le \ldots C_M$, so that the ordering of supervisors is consistent
with respect to both cost and skill level. We consider the problem of minimizing the expected surrogate loss of a
trained policy with respect to the most skilled supervisor $S_M$ in the hierarchy while minimizing the overall training
cost. In particular, this paper provides an empirical study of greedy combinations of three types of supervisors $S_1,
S_2, S_3$ for grasping in clutter which are applied in order to train a policy parameterized by a deep neural network.
Here, $S_1$ is an analytical motion planning algorithm with a cost $C_1=XX$, $S_2$ a supervisor
consisting a crowd-sourced Amazon Mechanical Turk laborers with $C_2=YY$, and $S_3$ a skilled human supervisor with
$C_3=ZZ$.

\section{Approach and Background}
 \subsection{Details on DAgger: Dataset Aggregation}
Since the cumulative expected reward of a policy is difficult to optimize directly,
DAgger~\cite{ross2010reduction} instead solves the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1)
computing the policy parameter $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states.

@@

 \subsubsection{Step 2}
The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
{\color{blue}FP: can we just have a neat algorithm box here?}
%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}
